Approximate Bayesian Computation in Large Scale Structure: constraining the galaxy-halo connection

### 2017-03-08 ccppabc/text/revision/main.tex
struggling with merge conflict still

Furthermore, {\em ABC-PMC -- unlike the Gaussian pseudo-likelihood approach -- 
is agnostic about the functional form of the underlying distribution of the 
summary statistics} 
($\xigg$ and $\gmf$). 
{\bf \color{darkgreen}
CHH: Need a sentence here that reiterates that the Gaussian functional form 
assumption is incorrect and especially incorrect for the GMF observable case.
Also, for us to say the following sentence, we need to talk about it more explicitly 
when discussing Figures 7,8,9, and 10. 
}
This may explain why we find less biased constraints from the
ABC-PMC analysis compared to the Gaussian-likelihood analysis, when using $\gmf(N)$ as an observable 
(Figures \ref{fig:hist_nbargmf} and \ref{fig:cont_nbargmf}).

>>>>

Furthermore, {\em ABC-PMC -- unlike the Gaussian pseudo-likelihood approach -- 
is agnostic about the functional form of the underlying distribution of the 
summary statistics} 
($\xigg$ and $\gmf$). 
{\bf \color{darkgreen}
CHH: Need a sentence here that reiterates that the Gaussian functional form 
assumption is incorrect and especially incorrect for the GMF observable case.
Also, for us to say the following sentence, we need to talk about it more explicitly 
when discussing Figures 7,8,9, and 10. 
}

{\bf \color{dred}
It is possible to consider a scenario in which the results from the standard analysis are inconsistent with the results from the ABC. Let us consider a dataset---from a galaxy survey---consisting of objects with different data qualities, signal-to-noise ratios, and systematic effects. This could be a catalog of galaxies which is incomplete beyond a certain luminosity or redshift. Another example could be a catalog with a singal-to-noise ratio cut. 
}

{\bf \color{dred}
In standard likelihood analyses, these selection effects, if not accounted for, can lead to biases in the inferred parameters of interest. Hierarchical models can modify the likelihood functions through by taking into account the selection effects. Alternatively, one could alleviate this issue by employing ABC equipped with a generative forward model of the data that incorporates signal-to-noise ratio cuts, incompleteness, etc.
}{\bf \color{darkgreen}
MJV: @CHH Can you read the two paragraphs above and see if they address referee's concern about the extreme data situation that could lead to discrepancy ?
}
%%%

%In general, we find that the constraints from ABC-PMC are consistent with those from the Gaussian-likelihood 
%MCMC method both in terms of accuracy and precision. However, we emphasize some advantages of using 
%ABC-PMC. ABC-PMC utilizes a forward generative model. Our forward generative model, for instance, 
%accounts for sample variance. In principle, they also have the advantage that they can account for 
%sources of systematic uncertainties in the observational data.

%%%
{\bf \color{darkgreen}
MJV: @CHH I think this paragraph is misleading since both ABC and Gaussian likelihood covariances suffer from inaccuracy of the simulations. I say we remove this paragraph entirely. It does not add any clarify anything. It just causes confusion!
}
{\bf \color{darkgreen} 
CHH: @MJV I'm not a big fan of this entire paragraph. The accuracy of the covariance
matrix depends on the accuracy of the mock catalogs (a.k.a. the forward model). While it's definitely 
true that on small scales they break down, forward models in ABC suffers from the same issues.
} 
%%%
Furthermore, the Gaussian-likelihood  approach relies on constructing an accurate covariance matrix
estimate that captures the sample variance of the data. While we are able to do this accurately 
within the scope of the HOD framework, for more general LSS parameter inference situations, it 
is both labor and computationally expensive and dependent on the accuracy of simulated mock catalogs,
which are known to be unreliable on small scales (see \citealt{cosmiccode,nifty} and references therein). 
Since ABC-PMC utilizes a forward model to account for sample variance, it does not depend on a 
covariance matrix estimate; hence it does not face these problems.

{\em ABC-PMC -- unlike the Gaussian-likelihood approach -- is agnostic about the functional form of the 
underlying distribution of the summary 
statistics} ($\xigg$ and $\gmf$). This may explain why we find less biased constraints from the
>>>>>>> afd43473184a6a4637881fb3504a38a867b27226
ABC-PMC analysis compared to the Gaussian-likelihood analysis, when using $\gmf(N)$ as an observable 
(Figures \ref{fig:hist_nbargmf} and \ref{fig:cont_nbargmf}).
